Tables in the project

### 2018-08-06 paper/Chapters/Chapter3.tex
tab1 hyper tab1 BMi

	\caption{\label{tab:daylevel}Day level latent class solution for three classes LCA model. (No Individual level Model)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{llccccc}
		\hiderowcolors
		\toprule
		\textbf{Time slots of} & \textbf{Responses to} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}}\\
		\midrule
		\showrowcolors
		6 am – 9 am &  &  &  &  &  & \\
		& Not eating any food & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.130 & 0.267 & 0.128\\
		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
		9 am – 12 am &  &  &  &  &  & \\
		& Not eating any food & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
		12 noon – 2 pm &  &  &  &  &  & \\
		& Not eating any food & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.560\\
		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
		2 pm – 5 pm &  &  &  &  &  & \\
		& Not eating any food & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
		5 pm – 8 pm &  &  &  &  &  & \\
		& Not eating any food & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.590 & 0.639\\
		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.370 & 0.211 & 0.328\\
		8 pm – 10 pm &  &  &  &  &  & \\
		& Not eating any food & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
		10 pm – 6 am &  &  &  &  &  & \\
		& Not eating any food & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
		\bottomrule
		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{7}{l}{\scriptsize \textbf{Abbreviation:} LCA, latent class analysis}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed $<$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed $\geqslant$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{}\\ 
	\end{tabular}
\end{table}

@@

>>>>

	\caption{\label{tab:daylevel}Day level latent class solution for three classes LCA model. (No individual level model)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{llccccc}
		\hiderowcolors
		\toprule
		\textbf{Time slots of} & \textbf{Responses to} & \multicolumn{1}{c}{ } & \multicolumn{1}{c}{ } & \textbf{\Centerstack{Class 1\\(39.5\%)}} & \textbf{\Centerstack{Class 2\\(20.4\%)}} & \textbf{\Centerstack{Class 3\\(40.1\%)}} \\
		\cmidrule(l{2pt}r{2pt}){5-5} \cmidrule(l{2pt}r{2pt}){6-6} \cmidrule(l{2pt}r{2pt}){7-7}
		 \textbf{the day} &  \textbf{carbohydrate intake} & $n$ & (\%) & \textbf{\Centerstack{High carbo- \\ hydrate day}} & \textbf{\Centerstack{Low carbo-\\hydrate day}} & \textbf{\Centerstack{Regular\\meals day}}\\
		\midrule
		\showrowcolors
		6 am – 9 am &  &  &  &  &  & \\
		& Not eating any food & 7655 & 31.2 & 0.129 & 0.450 & 0.320\\
		& Carbohydrate $<$ 50\%\textsuperscript{*} & 4500 & 18.4 & 0.130 & 0.267 & 0.128\\
		& Carbohydrate $\geqslant$ 50\%\textsuperscript{\dag} & 12328 & 50.4 & 0.741 & 0.283 & 0.552\\
		9 am – 12 am &  &  &  &  &  & \\
		& Not eating any food & 5447 & 22.2 & 0.237 & 0.079 & 0.401\\
		& Carbohydrate $<$ 50\% & 7227 & 29.5 & 0.158 & 0.492 & 0.173\\
		& Carbohydrate $\geqslant$ 50\% & 11809 & 48.2 & 0.605 & 0.429 & 0.426\\
		12 noon – 2 pm &  &  &  &  &  & \\
		& Not eating any food & 4783 & 19.5 & 0.156 & 0.356 & 0.019\\
		& Carbohydrate $<$ 50\% & 11112 & 45.4 & 0.405 & 0.413 & 0.560\\
		& Carbohydrate $\geqslant$ 50\% & 8588 & 35.1 & 0.439 & 0.231 & 0.421\\
		2 pm – 5 pm &  &  &  &  &  & \\
		& Not eating any food & 6926 & 28.3 & 0.130 & 0.123 & 0.659\\
		& Carbohydrate $<$ 50\% & 8277 & 33.8 & 0.249 & 0.602 & 0.076\\
		& Carbohydrate $\geqslant$ 50\% & 9280 & 37.9 & 0.621 & 0.276 & 0.266\\
		5 pm – 8 pm &  &  &  &  &  & \\
		& Not eating any food & 3043 & 12.4 & 0.114 & 0.199 & 0.034\\
		& Carbohydrate $<$ 50\% & 14240 & 58.2 & 0.516 & 0.590 & 0.639\\
		& Carbohydrate $\geqslant$ 50\% & 7200 & 29.4 & 0.370 & 0.211 & 0.328\\
		8 pm – 10 pm &  &  &  &  &  & \\
		& Not eating any food & 8722 & 35.6 & 0.322 & 0.291 & 0.480\\
		& Carbohydrate $<$ 50\% & 8898 & 36.3 & 0.266 & 0.551 & 0.212\\
		& Carbohydrate $\geqslant$ 50\% & 6863 & 28.0 & 0.412 & 0.158 & 0.308\\
		10 pm – 6 am &  &  &  &  &  & \\
		& Not eating any food & 16295 & 66.6 & 0.680 & 0.590 & 0.751\\
		& Carbohydrate $<$ 50\% & 4144 & 16.9 & 0.074 & 0.294 & 0.101\\
		& Carbohydrate $\geqslant$ 50\% & 4044 & 16.5 & 0.246 & 0.115 & 0.148\\
		\bottomrule
		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{7}{l}{\scriptsize \textbf{Abbreviation:} LCA, latent class analysis}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Carbohydrate $<$ 50\% indicates that within the time slot, carbohydrate contributed $<$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Carbohydrate $\geqslant$ 50\% indicates that within the time slot, carbohydrate contributed $\geqslant$ 50\% total energy intake.}}\\
		\multicolumn{7}{l}{}\\ 
	\end{tabular}
\end{table}

@@

\begin{sidewaystable}
%\begin{table}
	\caption{\label{tab:tab1hypetension}Weighted means, percentages, and 95 \% CIs of the characteristics by hypertension status in the UK adults. \\(NDNS RP 2008/09-2015/16, sample size = 6155)}
	\begin{tabular}[t]{lcccccc}
		\multicolumn{1}{c}{ } & \multicolumn{3}{c}{\textbf{Men (n = 2537)}} & \multicolumn{3}{c}{\textbf{Women (n = 3618)}} \\
		\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
		& \textbf{Non-hypertensive} & \textbf{Hypertensive} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{Non-hypertensive} & \textbf{Hypertensive} & \textbf{\textit{P} value\textsuperscript{*}}\\
		Weighted prevalence (\%) & 69.6 (66.6, 72.5)  & 30.4 (27.5, 33.4) &  & 72.5 (69.8, 75.0) & 27.5 (25.0, 30.2) & \\
		Age (years) & 43.2 (41.7, 44.7) & 59.9 (58.0, 61.7) & < 0.001 & 43.9 (42.7, 45.1) & 64.9 (63.4, 66.5) & < 0.001\\
		Country (\%) &  &  & 0.109 &  &  & 0.631\\
		\hspace{1em}England & 84.7 (80.9, 87.2) & 85.4 (81.2, 88.8) &  & 84.0 (81.0, 86.6) & 83.5 (79.1, 87.0) & \\
		\hspace{1em}Northern Ireland & 3.3 (2.2, 4.8) & 1.6 (0.8, 3.1) &  & 2.5 (1.9, 3.5) & 2.6 (1.5, 4.3) & \\
		\hspace{1em}Scotland & 8.6 (6.3, 11.7) & 7.1 (4.6, 10.9) &  & 8.7 (6.5, 11.7) & 7.9 (5.1, 11.8) & \\
		\hspace{1em}Wales & 3.9 (2.7, 5.6) & 5.9 (4.0, 8.5) &  & 4.7 (3.7, 6.0) & 6.1 (4.3, 8.6) & \\
		Ethnicity (\%) &  &  & 0.534 &  &  & 0.126\\
		\hspace{1em}White & 89.6 (86.5, 92.0) & 91.1 (86.2, 94.4) &  & 85.7 (82.7, 88.3) & 90.2 (85.0, 93.7) & \\
		\hspace{1em}Non-white & 10.4 (8.0, 13.5) & 8.9 (5.6, 13.8) &  & 14.3 (11.7, 17.3) & 9.8 (6.3, 15.0) & \\
		Education (\%) &  &  & 0.006 &  &  & < 0.001\\
		\hspace{1em}Degree or higher & 30.3 (26.6, 34.2) & 21.5 (17.3, 26.5) &  & 33.0 (29.9, 36.3) & 19.7 (15.8, 24.3) & \\
		\hspace{1em}Lower than Degree & 69.7 (65.8, 73.4) & 78.5 (73.5, 82.7) &  & 67.0 (63.7, 70.1) & 80.3 (75.7, 84.2) & \\
		Smoking status &  &  & < 0.001 &  &  & < 0.001\\
		\hspace{1em}Current & 19.7 (16.6, 23.1) & 12.9 (9.5, 17.2) &  & 15.2 (13.1, 17.6) & 8.5 (6.2, 11.6) & \\
		\hspace{1em}Ex-smoker & 24.2 (21.1, 27.6) & 38.8 (33.4, 44.5) &  & 21.6 (19.1, 24.4) & 32.2 (27.3, 37.4) & \\
		\hspace{1em}Never & 56.2 (52.1, 60.1) & 48.3 (42.7, 54.0) &  & 63.2 (60.1, 66.2) & 59.3 (54.0, 64.4) & \\
		Physical
		activity (hours/day) \textsuperscript{\dag} & 1.52 (1.33, 1.72) & 1.29 (1.08, 1.53) & 0.134 & 0.81 (0.73, 0.89) & 0.53 (0.42, 0.64) & < 0.001\\
		BMI (kg/m\textsuperscript{2}) & 26.8 (26.4, 27.2) & 29.5 (28.9, 29.9) & < 0.001 & 26.4 (26.1, 26.8) & 29.8 (29.2, 30.5) & < 0.001\\
		WC (cm) & 95.0 (93.9, 96.2) & 104.6 (103.2, 106.1) & < 0.001 & 85.7 (84.8, 86.6) & 95.7 (94.2, 97.2) & < 0.001\\
		Carbohydrate eating patterns (\%) &  &  & < 0.001 &  &  & < 0.001\\
		\hspace{1em}Low & 28.3 (24.8, 32.2) & 37.1 (32.0, 42.5) &  & 26.9 (24.1, 29.9) & 32.0 (27.2, 37.2) & \\
		\hspace{1em}Moderate & 30.8 (26.9, 35.0) & 19.3 (15.3, 24.1) &  & 29.6 (26.4, 33.0) & 18.4 (14.5, 22.9) & \\
		\hspace{1em}High & 40.8 (36.9, 44.9) & 43.6 (38.2, 49.2) &  & 43.5 (40.3, 46.8) & 49.7 (44.1, 55.2) & \\
		Total energy intake (kJ) & 9021.4 (8791.9, 9251.0) & 8366.2 (8094.9, 8637.4) & < 0.001 & 6802.6 (6681.1, 6924.0) & 6396.7 (6217.1, 6576.2) & < 0.001\\
		Carbohydrate intake (g) & 259.2 (252.9, 265.3) & 235.3 (227.8, 242.8) & < 0.001 & 198.0 (194.2, 201.8) & 184.5 (178.8, 190.1) & < 0.001\\
		\multicolumn{7}{l}{\textit{Note: }}\\
		\multicolumn{7}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
		\multicolumn{7}{l}{ BMI body mass index; WC, waist circumference.}\\
		\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
		\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an \textit{F} test for continuous variables or design-adjusted Pearson $\chi^2$ test.}\\
		\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
	\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}
	\rowcolors{2}{gray!6}{white}

%	\begin{table}

		\caption{\label{tab:tab1BMI}Weighted means, percentages, and 95 \% CIs of the characteristics by BMI categories in the UK adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
		\begin{tabular}[t]{lcccccccc}
			\multicolumn{1}{c}{ } & \multicolumn{4}{c}{\textbf{Men (n = 2537)}} & \multicolumn{4}{c}{\textbf{Women (n = 3618)}} \\
			\cmidrule(l{2pt}r{2pt}){2-5} \cmidrule(l{2pt}r{2pt}){6-9}
			& \textbf{Normal weight} & \textbf{Overweight} & \textbf{Obese} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{Normal weight} & \textbf{Overweight} & \textbf{Obese} & \textbf{\textit{P} value\textsuperscript{*}}\\
			Weighted prevalence (\%) & 30.9 (28.0, 33.9) & 43.4 (40.4, 46.4) & 25.7 (23.2, 28.4) &  & 41.7 (39.0, 44.4) & 30.9 (28.4, 33.5) & 27.4 (25.1, 29.9) & \\
			BMI (kg/m\textsuperscript{2}) & 22.6 (22.3, 22.8) & 27.3 (27.2, 27.5) & 33.7 (33.3, 34.2) & < 0.001 & 22.2 (22.0, 22.4) & 27.3 (27.2, 27.5) & 35.0 (34.6, 35.4) & < 0.001\\
			WC (cm) & 84.5 (83.6, 85.4) & 97.1 (96.4, 97.8) & 112.7 (111.6, 113.9) & < 0.001 & 76.9 (76.2, 77.5) & 89.0 (88.3, 89.7) & 103.7 (102.6, 104.7) & < 0.001\\
			Age (years) & 40.3 (38.2, 42.4) & 49.6 (47.9, 51.2) & 50.4 (48.5, 52.3) & < 0.001 & 45.0 (43.4, 46.7) & 50.4 (48.6, 52.3) & 50.9 (49.1, 52.7) & < 0.001\\
			Country (\%) &  &  &  & 0.236 &  &  &  & 0.589\\
			\hspace{1em}England & 83.9 (79.2, 87.7) & 86.9 (83.6, 89.7) & 81.6 (76.7, 85.7) &  & 84.3 (80.4, 87.5) & 83.7 (79.7, 87.0) & 82.4 (78.2, 85.9) & \\
			\hspace{1em}Northern Ireland & 3.3 (1.9, 5.8) & 2.3 (1.4, 3.6) & 3.2 (2.0, 4.9) &  & 3.0 (2.1, 4.2) & 2.2 (1.5, 3.2) & 3.4 (2.3, 5.0) & \\
			\hspace{1em}Scotland & 9.1 (6.1, 13.5) & 6.5 (4.4, 9.7) & 9.0 (5.9, 13.3) &  & 9.0 (6.1, 13.0) & 9.0 (6.3, 12.8) & 8.5 (5.7, 12.6) & \\
			\hspace{1em}Wales & 3.7 (2.3, 5.8) & 4.3 (3.1, 5.9) & 6.3 (4.0, 9.7) &  & 3.8 (2.9, 5.1) & 5.1 (3.6, 7.2) & 5.7 (4.2, 7.7) & \\
			Ethnicity (\%) &  &  &  & 0.466 &  &  &  & 0.879\\
			\hspace{1em}White & 88.7 (83.9, 92.2) & 89.1 (85.6, 91.9) & 91.9 (87.3, 94.9) &  & 88.4 (84.9, 91.19 & 88.6 (84.5, 91.7) & 87.3 (82.5, 90.9) & \\
			\hspace{1em}Non-white & 11.3 (7.8, 16.1) & 10.9 (8.1, 14.4) & 8.1 (5.1, 12.7) &  & 11.6 (8.9, 15.1) & 11.4 (8.3, 15.5) & 12.7 (9.1, 17.5) & \\
			Education (\%) &  &  &  & 0.022 &  &  &  & < 0.001\\
			\hspace{1em}Degree or higher & 29.5 (24.5, 35.0) & 28.3 (24.3, 32.7) & 20.1 (16.0, 25.0) &  & 35.7 (31.8, 39.8) & 24.2 (20.4, 28.4) & 19.4 (16.1, 23.2) & \\
			\hspace{1em}Lower than Degree & 70.5 (65.0, 75.5) & 71.7 (67.3, 75.7) & 79.9 (75.0, 84.0) &  & 64.3 (60.2, 68.2) & 75.8 (71.6, 79.6) & 80.6 (76.8, 83.9) & \\
			Smoking status &  &  &  & < 0.001 &  &  &  & 0.042\\
			\hspace{1em}Current  & 32.0  (26.8, 37.7) & 18.7 (15.5, 22.4) & 19.2 (15.0, 24.3) &  & 19.5 (16.4, 22.9) & 17.8 (14.8, 21.4) & 16.4 (13.1, 20.3) & \\
			\hspace{1em}Ex-smoker & 17.3 (13.5, 22.0) & 28.6 (24.8, 32.7) & 32.9 (27.9, 38.4) &  & 19.0 (15.9, 22.5) & 24.4 (20.8, 28.3) & 26.9 (22.8, 31.6) & \\
			\hspace{1em}Never & 50.6 (44.8, 56.4) & 52.7 (48.2, 57.1) & 47.9 (42.1, 53.7) &  & 61.6 (57.4, 65.5) & 57.8 (53.3, 62.2) & 56.7 (51.8, 61.4) & \\
			Physical activity\textsuperscript{\dag} (hours/day) & 1.58 (1.33, 1.85) & 1.42 (1.24, 1.62) & 1.41 (1.15, 1.70) & 0.547 & 0.84 (0.74, 0.94) & 0.71 (0.62, 0.79) & 0.65 (0.53, 0.78) & 0.038\\
			Carbohydrate eating patterns (\%) &  &  &  & 0.072 &  &  &  & 0.253\\
			\hspace{1em}Low & 25.9 (21.0, 31.5) & 30.6 (26.6, 35.0) & 31.4 (26.6, 36.6) &  & 24.8 (21.5, 28.5) & 26.8 (22.8, 31.2) & 29.5 (25.3, 34.1) & \\
			\hspace{1em}Moderate & 34.2 (28.6, 40.4) & 25.5 (21.9, 29.6) & 25.5 (20.6, 31.0) &  & 27.6 (23.8, 31.8) & 26.3 (22.3, 30.8) & 29.8 (25.4, 34.6) & \\
			\hspace{1em}High & 39.9 (34.2, 45.8) & 43.8 (39.6, 48.2) & 43.1 (37.7, 48.7) &  & 47.6 (43.3, 51.9) & 46.9 (42.4, 51.4) & 40.7 (36.0, 45.6) & \\
			Total energy intake (kJ) & \Centerstack{9351.2 \\ (8961.7, 9740.7)} & \Centerstack{8786.9 \\ (8595.1, 8978.7)} & \Centerstack{8465.3 \\ (8196.4, 8734.1)} & 0.001 & \Centerstack{7048.9 \\ (6894.4, 7203.4)} & \Centerstack{6570.1 \\(6406.2, 6734.0)} & \Centerstack{6566.4 \\ (6360.7, 6772.1)} & < 0.001\\
			Carbohydrate intake (g) & \Centerstack{268.7 \\ (258.3, 279.2)} & \Centerstack{250.1\\ (244.1, 256.1)} & \Centerstack{239.1 \\ (231.3, 246.8)} & < 0.001 & \Centerstack{205.8 \\(200.2, 211.3)} & \Centerstack{190.1 \\ (185.3, 194.9)} & \Centerstack{189.8 \\ (183.7, 195.9)} & < 0.001\\
			\multicolumn{9}{l}{\textit{Note: }}\\
			\multicolumn{9}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;}\\
			\multicolumn{9}{l}{ BMI body mass index; WC, waist circumference.}\\
			\multicolumn{9}{l}{Variables are weighted by nurse visiting weights.}\\
			\multicolumn{9}{l}{\textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)} \\ 
			\multicolumn{9}{l}{for continuous variables or design-adjusted Pearson $\chi^2$ test}\\
			\multicolumn{9}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
		\end{tabular}
%	\end{table}

	\rowcolors{2}{white}{white}
\end{sidewaystable}

### 2018-08-06 paper/Tables/2by2Table1.Rmd
tables figs of MLCA done, classes and bmi, dm, hyt estimates needed
tab1 hyper tab1 BMi

# 
dt[9, 1] <- c("Hypertension[note] (%)")
dt[12, 1] <- c("Carbohydrate percent[note] (%)")

@@

>>>>

# 
dt[9, 1] <- c("Hypertension[note] (%)")
dt[13, 1] <- c("Carbohydrate percent[note] (%)")

@@

## Hypertension table 1

```{r tab1hypetension, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensiontab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Non-hypertensive", "Hypertensive", "P value[note]", 
               "Non-hypertensive", "Hypertensive", "P value")

# 
# dt[9, 1] <- c("Hypertension[note] (%)")
# dt[13, 1] <- c("Carbohydrate percent[note] (%)")

dt[17, 1] <- c("Physical\nactivity (hours/day) [note]")
# dt[20, 1] <- c("DM [note]")
# dt[20, 1] <- c("Paid employment[note] (%)")
# dt[23, 1] <- c("Live with partner[note] (%)")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(3:6,8,9,11,12,14,15,16,21:23)) %>% 
   add_header_above(c(" ", "Men (n = 2537)" = 3, "Women (n = 3618)" = 3)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",
                        " BMI body mass index; WC, waist circumference.", 
                        "Variables are weighted by nurse visiting weights.")) %>% 
  add_footnote(c("Significant sex-specific differences by hypertension status assessed using an F test for continuous variables or design-adjusted Pearson chi-square test",
                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 # "DM was defined by A1C > 6.5%.",
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
                 ), 
               notation = "symbol")
```

## BMI

```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")

# 
# dt[9, 1] <- c("Hypertension[note] (%)")
# dt[13, 1] <- c("Carbohydrate percent[note] (%)")

dt[17, 1] <- c("Physical\nactivity (hours/day) [note]")
# dt[20, 1] <- c("DM [note]")
# dt[20, 1] <- c("Paid employment[note] (%)")
# dt[23, 1] <- c("Live with partner[note] (%)")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
                       " BMI body mass index; WC, waist circumference.", 
                       "Variables are weighted by nurse visiting weights.")) %>% 
  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 # "DM was defined by A1C > 6.5%.",
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
                 ), 
               notation = "symbol")
```

## DM

```{r tab1BMI, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/BMItab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Normal weight", "Overweight", "Obese", "P value[note]", "Normal weight", "Overweight", "Obese", "P value")

# 
# dt[9, 1] <- c("Hypertension[note] (%)")
# dt[13, 1] <- c("Carbohydrate percent[note] (%)")

dt[17, 1] <- c("Physical\nactivity (hours/day) [note]")
# dt[20, 1] <- c("DM [note]")
# dt[20, 1] <- c("Paid employment[note] (%)")
# dt[23, 1] <- c("Live with partner[note] (%)")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
                       " BMI body mass index; WC, waist circumference.", 
                       "Variables are weighted by nurse visiting weights.")) %>% 
  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 # "DM was defined by A1C > 6.5%.",
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
                 ), 
               notation = "symbol")
```
